Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-10-30 journal/ms.Rmd
journal

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.

@@

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
library(HDInterval)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.  The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975). Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017] add Beckage, 2011 and other people...

@@

```{r growth, fig.cap = "Illustration of the two growth scenarios. Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node E1 is more likely to enter the lexicon first. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("figs/growth2.png")
```

@hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT. This finding, though potentially very profound, has only been estabished in the special case of networks that are based on 1) semantic associations,  2) word production as a measure of acquisition, and 2) data from English-learning children, only. The extent to which this result depends on the domain, the measure and culture/languagae is still unclear. In this work, we test the generality of the finding along these three dimesnions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is strcutured. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also influence word learning? Previous work did find an effect of words' connectivity in the phonological network on their age of learning (Storkel, 2004, 2009; Stokes 2014). In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life. However, as mentioned above, this finding did not examine the underlying learning mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.} Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

Second, we study vocabularies measured using both comprehension and production. Previous studies have found differences between these vocabularies in terms of their content and rate of acquistion (Benedict, 1979; Fensen et al. 1993). These differences can be due to the fact that comprehension and production do not share the same contraints. For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends additionally on the ease with witch words are articuated (e.g., shorter words are produced earlier, Braginsky et al. 2016). By including comprehension-based vocabularies in our analysis, we assess the extent to which the network growth mechanisms capture general learning patterns beyond the specific constraints of production.

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-lingustic variability along both the semantic and phonological domains (Youn et al. 2015; Arbesman et al. 2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.} Besides, cultures might differ in the way caregivers guide the chidlren's learning patterns or in the way the adults' linguistic input is organized (Kuhl et al., 1997; Cristia et al. 2017), and this difference could influecne the learning mechanism. Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechansism is specific to some patterns of learning that emerge due to the particulars of a given language or culture (Bates & MacWhinney, 1987; Slobin, 1985).

HERE ORGANIZATION OF THE PAPER

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child “understands” (comprehension) or “understands and says” (production) for each of about 400 words. For youner chidlren (between 8 and 18 months), both comprehension and production are queried, whereas for oder chidlren (between 16 to 36 months) only production is queried. We use data from younger chidlren to test comprehension and data from older chidlren to test production. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns. Table \@ref(tab:stats) gives an overview of the data source.

## Age of acquisition
For each word in CDI data, we compute the proportion of children who understand or produce the word at each month. Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at lest 50% of chidlren know the word. We take this point in time to be each word’s age of acquisition [@goodman2008] and Braginsky.

<!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \@ref(tab:stats) gives an overview of the data used. -->

@@

statistics <- feather::read_feather("../saved_data/statistics.feather") 
rownames(statistics) <- NULL

tab <- xtable::xtable(statistics,
                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")

print(tab, type="latex", comment = F, table.placement = "H")

#print(statistics, type="latex", comment = F, table.placement = "H")
```

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

Free Association norms are available only in English. We used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages. Note that this does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly. Though using the same association data acoss langauges assumes that the semantic similarity measure is universal (which is a reasonable approximation, Youn et al. 2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possbility different learing strategies.

@@

To construct phonological networks we first mapped the orthogrphic transcrition of words to their International Phonetic Alphabet (IPA) transcriptions, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1. When using this threshold, the resulting networks were too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2. The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that are relevant to INT and/or EXT.

@@

@@

```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of a EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic networks). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier. HERE MENTION THE AVERAGE VALUE OF THE CORRELATIONS

@@

```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. The figure shows the results for both production and comprehension data. A perfect power-law distribution should appear as a straight line in this graph."}

knitr::include_graphics("figs/plot_degree.pdf")

@@

We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99]. If the network displays this property, this fact would suggest a INT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT. The log-log plots are shown in Figure \@ref(fig:degreeDist). We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].

In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$. Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.

The results are shown in table XX. Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1. Also talk about the fact that the power law is truncated.

@@

```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks. Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals. Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

@@

### How does each growth scenario predict noun development?

To test the network growth scenarios, we fit different growth models to the data. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}

\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient). A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \@ref(fig:growth) for an illustration of how growth values $d_i$ are defined in each growth scenario). The normalization includes all words that could be learned at that month.

@@

The results replicate Hills et al.'s finding regarding the semantic netowrk in English and prouction data, which is that this network grows by EXT, not by INT. Besides, this finding generalize to comprehension, and holds overall across languages. One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our intial approximation, albeit a posteriori, about the unversisality of the semantic similarity measure. In the phonological domain, the EXT model also fits better the data than INT for both production and comprehension. Similar to the sematic domain, the findings generalize well cross-linguistically.

@@

plot_static_preds <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(0,0.2))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

@@

```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined regression model. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

>>>>

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.

@@

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
library(HDInterval)
library(kableExtra)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.  The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975). Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].

@@

```{r growth, fig.cap = "Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
knitr::include_graphics("figs/growth3.png")
```

@hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT. This finding, though potentially very profound, has only been established in the special case of networks that are based on 1) semantic associations,  2) production-based vocabularies, and 2) data from English-learning children, only. The extent to which this result depends on the domain, the measure and culture/language is still unclear. In this work, we test the generality of the finding along these three dimensions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is structured. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also influence word learning? Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014]. In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life. However, this finding is compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.  Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

Second, we study vocabularies measured using both comprehension and production. Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94]. These differences may reflect the fact that comprehension and production do not share the same constraints. For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2016]. By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.} Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the chidlren's learning strategy. Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].

The paper is organized as follows. First, we describe the datasets we used and explain how we constructed the networks. Second, we analyze static properties of words' connectivity in these networks (correlation with AoA and shape of the distribution) and we explain how these properties infom hypotheses about network growth. Next, we explicitly fit the two hypothesized growth mechanisms to the data. We investigate the extent to which the results obtained in @hills2009 generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. We use data from younger children to test comprehension and data from older children to test production across 10 languages. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns. Table \@ref(tab:stats) gives an overview of the data.

## Age of acquisition
For each word in the CDI data, we compute the proportion of children who understand or produce the word at each month. Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50% of children know the word. We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky2016].
<!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \@ref(tab:stats) gives an overview of the data used. -->

@@

statistics <- feather::read_feather("../saved_data/stats_new.feather") 
#rownames(statistics) <- NULL

kable(statistics, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for data from Wordbank.",
      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages. Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly. Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption (e.g., Youn et al. 2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.

@@

To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017]. However, these studies reported a contribution of phonological networks to word learning when these networks were built using a rich adult vocabulary. However, since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary which, nevertheless, contains very few word pairs with an edit distance of 1. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker that those done with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that are relevant to INT and/or EXT.  In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had both semantic and phonological information in each language.

@@

corrAve <- correlations %>%
  group_by(measure, predictor) %>%
  summarise(ave = mean(cor),
            sd = sd(cor))

#Average values of the correlation 
pp_ave=corrAve$ave[which(corrAve$measure == "produces" & corrAve$predictor == "Phono")]
ps_ave=corrAve$ave[which(corrAve$measure == "produces" & corrAve$predictor == "Sem")]
cp_ave=corrAve$ave[which(corrAve$measure == "understands" & corrAve$predictor == "Phono")]
cs_ave=corrAve$ave[which(corrAve$measure == "understands" & corrAve$predictor == "Sem")]

#Sd of the ave 
pp_sd=corrAve$sd[which(corrAve$measure == "produces" & corrAve$predictor == "Phono")]
ps_sd=corrAve$sd[which(corrAve$measure == "produces" & corrAve$predictor == "Sem")]
cp_sd=corrAve$sd[which(corrAve$measure == "understands" & corrAve$predictor == "Phono")]
cs_sd=corrAve$sd[which(corrAve$measure == "understands" & corrAve$predictor == "Sem")]

@@

```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.", fig.width=8, fig.height=4}

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production and comprehension for each word varies as a function of its degree (or indegree for the semantic networks) as well as the correlation values. For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.

The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and extending these findings to ten different languages (with few exceptions) in both production- and comprehension-based vocabularies.

@@

```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. The figure shows the results for both production and comprehension data. A perfect power-law distribution should appear as a straight line in this graph.",  fig.width=10, fig.height=2}

#knitr::include_graphics("figs/plot_degree.pdf")
plot_degree
```

We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99]. If the network displays this property, this fact would suggest an INT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT. The log-log plots are shown in Figure \@ref(fig:degreeDist). We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using a related R package [poweRlaw, @gillespie15].

```{r powerLawData, results="asis", echo=FALSE}

powerL <- feather::read_feather("../saved_data/degree_test.feather") %>%
  rename(Kmin = xMin) %>%
  rename(pValue = pVal) %>%
  rename(domain = dimension) %>%
  mutate(alpha_r = round(alpha, digits = 2),
         pValue_r = round(pValue, digits = 3)) %>%
  select(Kmin, domain, language, measure, alpha_r, pValue_r)

powerProd <- powerL %>%
  dplyr::filter(measure == 'produces') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  spread(domain, data) %>%
  unnest(.sep = "_")

powerComp <- powerL %>%
  dplyr::filter(measure == 'understands') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  spread(domain, data) %>%
  unnest(.sep = "_")

#rownames(statistics) <- NULL 
```

```{r powerLawProd, results="asis", echo=FALSE}

kable(powerProd, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
      col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")
```

```{r powerLawComp, results="asis", echo=FALSE}

kable(powerComp, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Results of fitting a power law model to the degree distribution in each model for comprehension data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
      col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$. Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model. The results are shown in Table \@ref(tab:powerLawProd) for production data, and in Table \@ref(tab:powerLawComp) for comprehension data.

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks ––as well as the observed cross-linguistic variability in the value of the cut-offs–– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks. Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals. Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.", fig.width=8, fig.height=3}

@@

To test the network growth scenarios, we fit two growth models to the data. We calculated the probability that a word $w_i$, with a utility value $u_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta u_i}}{\sum_j e^{\beta u_j} }
\end{equation}

\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient). A positive value of $\beta$ means that words with higher utility values $u_i$ are acquired first, and a negative value means that words with lower utility values are acquired first (see Figure \@ref(fig:growth) for an illustration of how utilities values $u_i$ are defined in each growth scenario). The normalization includes all words that could be learned at that month.

@@

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaing, this finding generalizes to comprehension, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.

@@

plot_static_preds <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(-1,0,1))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

@@

```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}
